A Switching Planner for Combined Task and Observation Planning

### 2011-02-08 subarchitectures/planner.sa/trunk/src/latex/AAAI11/switching.tex
Revised text about state space abstraction

Because online DT planning in large problems is impractical (we seek
response times in seconds), a DT session plans in an abstract process
determined by the current trace and underlying belief-state. This
abstraction is constructed by first excluding all propositions (and
related actions) that are not true, or {\em assumed } true, of states
in the trace, then adding them back, using as an heuristic the entropy
of the trace assumptions conditional on a candidate
proposition. Propositions are added, one at a time, until the number
of states in the initial belief-state reaches a given
threshold.\footnote{Our experiments are performed using a number of
different threshold parameters.}  To the resulting abstract model we
also add {\em disconfirm} and {\em confirm} actions that the
DT session can schedule in order to judge an atomic assumption
in the trace. In the abstract model these actions yield a relatively
small reward if the corresponding judgement is true (or small penalty
otherwise). If a judgement action is scheduled for execution the
DT session is terminated, and control is returned to a
sequential session.

Finally, whether proceeding in a sequential or DT session, our
continual planner maintains a factored representation of successive
belief-states by performing belief revision. Our internal
representation of the underlying belief-state corresponds more-or-less
directly to an $(\pp{:init})$ declaration. That belief-state
distribution is used: (1) as the source of candidate determinisations
for sequential planning, (2) in determining when to switch to a DT
session, and (3) as a mechanism to guide construction of an abstract
process for DT sessions.

@@

The process posed to a DT session is abstract. The abstraction is
defined by first constructing an $(\pp{:init})$ declaration without
any-active assumptions from the trace -- e.g.,
(Fig.\ref{fig:abstraction-b}) gives an example, where diamonds are
probabilistic terms, and circles are atomic and/or conjunctive.
%%
For each excluded atom, we compute the {\em entropy} of the active
assumptions, {\em conditional} on that atom. Intuitively, lower
entropy indicates an atom gives better information about
assumptions. Facts are iteratively added to the belief-state in
increasing order according to that measure
(Fig.\ref{fig:abstraction-c}).

@@

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "moritz_2011"
%%% End:

>>>>

Because online DT planning in large problems is impractical (we seek
response times in seconds), a DT session plans in an abstract process
determined by the current trace and underlying belief-state. This
abstract problem is created by selecting only those propositions that
are \emph{relevant} to the subproblem the DT session is asked to
solve.
% MOG: Describe this in detail in the appropriate subsection
%  This
% abstraction is constructed by first excluding all propositions (and
% related actions) that are not true, or {\em assumed } true, of states
% in the trace, then adding them back, using as an heuristic the entropy
% of the trace assumptions conditional on a candidate
% proposition. Propositions are added, one at a time, until the number
% of states in the initial belief-state reaches a given
% threshold.\footnote{Our experiments are performed using a number of
% different threshold parameters.} 
To the resulting abstract model we
also add {\em disconfirm} and {\em confirm} actions that the
DT session can schedule in order to judge an atomic assumption
in the trace. In the abstract model these actions yield a relatively
small reward if the corresponding judgement is true (or small penalty
otherwise). If a judgement action is scheduled for execution the
DT session is terminated, and control is returned to the
sequential planner.

Finally, whether proceeding in a sequential or DT session, our
continual planner maintains a factored representation of successive
belief-states by performing belief revision. For that, we transform
the $(\pp{:init})$ declaration into a tree-shaped bayesian network
which gets updated whenever an actions is performed or an observation
is received. That belief-state representation is used:
(1) as the source of candidate determinisations for sequential
planning, (2) in determining when to switch to a DT session, and (3)
as a mechanism to guide construction of an abstract process for DT
sessions.

@@

As we are aiming to keep the decision theoretic session fast, we try
to keep the state space of the abstract problem as small as
possible. In a deterministic-action POMDP, the state space size is
determined by two factors: the number of non-zero states in the
initial belief-state and the number of executable actions. As
determining the relevance of an action for a given goal in in general
a hard problem, we concentrate on keeping the number of uncertain
facts as low as possible without losing important information about
the sensing goal.

We perform the abstraction of the belief space by first constructing
an $(\pp{:init})$ declaration which only contains relevant assumptions
from the trace -- e.g., (Fig.\ref{fig:abstraction-b}) gives an
example, where diamonds are probabilistic terms, and circles are
atomic and/or conjunctive.
%%
For each excluded atom, we compute the {\em entropy} of the active
assumptions, {\em conditional} on that atom. Intuitively, lower
entropy indicates an atom gives better information about
assumptions. Facts are iteratively added to the belief-state in
increasing order according to that measure until the belief space size
reaches a predefined limit or no more atoms that reduce the entropy
can be added (Fig.\ref{fig:abstraction-c}).

@@

% When limiting the number of actions, we aim to include those that are
% possibly required to a) reach the goal or b) to directly observe an
% atom that is part of the abstract belief state. In general, checking
% this for an action is \textsc{PSPACE} complete for \textsc{STRIPS}
% planning.

% We approximate the set of relevant actions as follows: Let
% \relevantAtoms\ be the set of atoms that either occur in the goal
% condition \poss(\switchAction) or in a precondition \poss($a$) of an
% action $a$ that can directly sense any atom in the abstract belief
% state. We construct a \emph{relaxed planning graph} with
% \relevantAtoms\ as goal atoms from which we extract a relaxed
% plan.

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "aaai11"
%%% End:
